\subsection{Modeling Numbers of Contacts}
\label{sec:number_of_contacts}

Consider a hypothetical population of 1,000 individuals in which 50 were infected with a
novel infectious disease. From this alone, it is impossible to say whether only
those 50 people had contact with an infectious person and the disease has an infection
probability of 1 per contact or whether everyone met an infectious person but the
disease has an infection probability of only 5 percent per contact. SEIR models do not
distinguish contact frequency from the infectiousness of each contact and
combine the two in one parameter that is not invariant to social distancing policies.

To model social distancing policies, we need to disentangle the effects of the number of
contacts of each individual and the effect of policy-invariant infection probabilities
specific to each contact type. Since not all contacts are equally infectious, we
distinguish different contact types.

The number and type of contacts in our model can be easily extended. Each type of
contacts is described by a function that maps individual characteristics, health states
and the date into a number of planned contacts for each individual. This allows to model
a wide range of contact types.

In our empirical application we distinguish the following  contact types that
are depicted in Figure~\ref{fig:model_contacts_infections} and can be further grouped
in the categories household, work, education and others.

types of contacts:\comment[id=HM]{I started updating this to understand it better myself.
In the end, I think it will be useful to group into HH / work / schools and add an
introductory sentence for each group. E.g., that work is for everybody who is working ---
except there is a different model for teachers (?), ...}

\begin{itemize}
    \item Households: Each household member meets all other household members every day.
    % Household sizes and structures are calibrated to be representative for Germany.


    \item Recurrent work contacts, capturing contacts with coworkers, repeating
          clients and superiors. Some of these recurrent contacts take place on
          every workday, others just once per week.

    \item Random work contacts: Working adults have contacts with randomly drawn other
          people, which are assortative in geographical location and age.


    \item Schools: Each student meets all of his classmates every day. Class sizes are
    calibrated to be representative for Germany and students have the same age. Schools
    are closed on weekends and during vacations, which vary by states. School classes
    also meet six teachers everyday and some of the teachers meet each other.

    \item Preschools: Children who are at least three years old and younger than six may
    attend preschool. Each group of nine children interacts with the same two adults
    every day. The children in each group are of the same age. The remaining mechanics
    are similar to schools.

    \item Nurseries: Children younger than three years may attend a nursery and interact
    with one adult. The age of the children varies within groups. The remaining
    mechanics are similar to schools.

    \item Random other contacts: Contacts with randomly drawn other
    people, which are assortative with respect to geographic location and and age group.
    This contact type reflects contacts during leisure activities, grocery shopping,
    medical appointments, etc..

    \item Recurrent other contacts representing contacts with friends neighbors or
        family members who do not live in the same household. Some of these contacts
        happen daily, others only once per week.


\end{itemize}

The number of random and recurrent contacts at the workplace, during leisure activities
and at home is calibrated with data provided by \citet{Mossong2008}. For details see
Section~\ref{subsec:data_number_of_contacts}. In particular, we sample the number of
contacts or group sizes from empirical distributions that sometimes depend on age. It
would also be possible to use economic or other behavioral models to predict the number
of contacts.

% Theoretically, each contact type can have its own infection probability. However, to
% reduce the number of free parameters and thus avoid a potential over-fitting we only
% estimate different infection probabilities for the areas work, school, preschool and
% nurseries, households and other contacts.
