\subsection{Reducing Numbers of Contacts via NPIs}
\label{sec:policies}

Our model makes it very easy to model a wide range of NPIs, either in isolation or
simultaneously. This is important for two reasons: Firstly, it allows to predict and
quantify the effect of novel NPIs. Secondly, it allows to model the actually implemented
policy environment in great detail, which is necessary to use use the full time series
of infections and fatality rates to estimate the model parameters.\footnote{
See \citet{Avery2020} for an explanation why it can be harmful to use too long time
series to estimate simple SEIR type models.}


Instead of thinking of policies as completely replacing how many contacts people have,
it is often more helpful to think of them as adjusting the pre-pandemic number of
contacts. Therefore, we implement policies as a step that happens after the number of contacts is
calculated but before individuals are matched.

On an abstract level, a policy is a functions that modifies the number of contacts of
one contact type. This function can be random or deterministic. For example, school
closures simply set all school contacts to zero. A work from home mandate leads to a
share of workers staying home every day whereas those who cannot work from home are
unaffected. Hygiene measures at work randomly reduce the number of infectious contacts
for all workers who still go to work.

Policies can also interact. For example, school vacations are temporally reducing school
contacts to zero while at the same time increasing other contacts to account for
increased leisure activities and family visits during this time. This is important to
reproduce the finding that school vacations do not reduce infection numbers even though
schools lead to infections when open \citep{Isphording2021}.

The most complex policies are typically found in the education sector. Since the
beginning of 2021 schools have switched back and fourth between full closures,
split class approaches with alternating schedules for some or all age groups and
reopening while maintaining hygiene measures. On top of that there are different
policies for allowing young students whose parents work full time to attend school
even on days where they normally would not. For details on how we calibrate these
policies see Section~\ref{subsec:policies_seasonality}.

Importantly, policies can depend on the health states of participating individuals.
This allows to quarantine entire school classes if one student tested positive or
to implement official or private contact tracing.

For some policies the exact effect on each contact type is not easy to determine. If
this refers to a policy has been active during the estimation period, it is possible to
estimate such parameters by fitting the model to time series data of infection rates.
This is only possible if the policy was not active during the whole estimation period
and thus the infection probabilities can be identified separately. We do this to account
for hygiene measures at school and in the workplace that have been in effect since
November 2020.
